Detecting Facial Expressions in Professional Tennis Matches

### 2016-12-14 Report06-12.Rmd
report
Updates

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: Stephanie Kobakian, Mitchell O'Hara Wild. Supervised by Dianne Cook, Stephanie
  Kovalcik
date: "November 19 2016"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
fontsize: 11pt
bibliography: references.bib
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
require(pander)
require(ggplot2)
require(imager)
require(devtools)
require(knitcitations)
require(RefManageR)
require(readr)
require(knitr)
require(grid)
require(tidyverse)
require(magick)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,cache=TRUE)

@@

setwd("C:/Users/steff/Github/face-recognition-presentation")

@@

#####**Table 1.** Scene Attributes
```{r T1 Scene Attributes Table}
kable(SceneAttributes, format = "pandoc", booktabs = TRUE)
```

@@

#####**Table 2.** Solution Specifications
```{r T2 Solution Specifications Table, results='asis'}
kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)

@@

#####**Table 3.** Face Attributes
```{r T3 Face Attribute Tables, results='asis'}
kable(FaceAttributes, format = "pandoc", booktabs = TRUE)

@@

####Data Manipulation
The collected data was spread across 6 files. See Appendices.
For each software we had the classified faces csv file, these are located in the appendix.
The collation of the results from the Manual Recognition Program created the files ManualClassifiedFaces and ManualClassifiedScenes.

>>>>

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: Stephanie Kobakian, Mitchell O'Hara Wild. Supervised by Dianne Cook, Stephanie
  Kovalcik
date: "November 19 2016"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_caption: yes
  word_document:
    toc: yes
fontsize: 11pt
bibliography: references.bib
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
require(pander)
require(ggplot2)
require(imager)
require(devtools)
require(knitcitations)
require(RefManageR)
require(readr)
require(knitr)
require(grid)
require(tidyverse)
require(magick)
require(kfigr)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,
                      cache=TRUE, fig.align = 'center')

@@

setwd("C:/Users/steff/Github/face-recognition")

@@

#####**Table 1.** Scene Attributes
```{r Scene-Attributes-Table, anchor="table"}
kable(SceneAttributes, format = "pandoc", booktabs = TRUE, caption = figr("Scene-Attributes-Table", TRUE, type="Table"))
```

`r figr("Scene-Attributes-Table", TRUE, type="Table")`   Yayyy

@@

#####**Table 2.** Solution Specifications
```{r Solution-Specifications-Table, results='asis', anchor="table"}
kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)

@@

#####**Table \label{tab:FAT}.** Face Attributes
```{r T3 Face Attribute Tables, results='asis'}
kable(FaceAttributes, format = "pandoc", booktabs = TRUE)
```

Table \ref{tab:FAT} above

@@

####Data Processing
The data was spread across 6 files. For each software we had the classified faces csv file, these are located in the appendix.
The collation of the results from the Manual Recognition Program created the files ManualClassifiedFaces and ManualClassifiedScenes.
